Appendix S1: Supporting Tables and Figures

### 2021-12-24 ms/SI.Rmd
Use equal-area projection for spatial data

```{r grain-size, fig.width = 7, fig.height = 3}
# Helper function to format resolution labels
degree_lab <- function (x) {
  as.numeric(x) %>% 
    scales::number(suffix = "\u00b0", accuracy = 0.1)
}

@@

# Percent of grid cells with redundancy > 0.5 by grain size
a <- ggplot(redundancy_summary, aes(x = res, y = percent_above_50)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = degree_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy > 0.5"
  )

# Percent of grid cells with redundancy = 0 by grain size
b <- ggplot(redundancy_summary, aes(x = res, y = percent_singletons)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = degree_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy = 0"
  )

# Distribution of redundancy by grain size
c <- ggplot(redundancy_by_res, aes(x = redundancy, y = res)) +
  geom_density_ridges(scale = 1.5) + 
  scale_y_discrete(expand = c(0, 0), labels = degree_lab) +     # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  labs(
    x = "Redundancy",
    y = "Resolution"
  )

@@

**`r s_figure("grain-size")`**. Effect of grain size on sampling redundancy. (a), Percent of grid cells with redundancy > 0.5 by grain size (0.1, 0.2, 0.3, or 0.4 degree grid-cells). (b), Percent of grid cells with redundancy = 0 by grain size. (c), Distribution of redundancy values by grain size. There is a sudden improvement in redundancy values from 0.1 to 0.2 degree grid-cells, but less improvement as grain size is increased beyond 0.2 degrees.

>>>>

```{r grain-size, fig.width = 7, fig.height = 3}
# Helper function to format resolution labels
km_lab <- function (x) {
  as.numeric(x) %>% 
    scales::number(suffix = "km", scale = 1e-3)
}

@@

# Percent of grid cells with redundancy > 0.5 by grain size
a <- ggplot(redundancy_summary, aes(x = res, y = percent_above_50)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = km_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy > 0.5"
  )

# Percent of grid cells with redundancy = 0 by grain size
b <- ggplot(redundancy_summary, aes(x = res, y = percent_singletons)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_discrete(labels = km_lab) +
  labs(
    x = "Resolution",
    y = "Redundancy = 0"
  )

# Distribution of redundancy by grain size
c <- ggplot(redundancy_by_res, aes(x = redundancy, y = res)) +
  geom_density_ridges(scale = 1.5) + 
  scale_y_discrete(expand = c(0, 0), labels = km_lab) + # will generally have to set the `expand` option
  scale_x_continuous(expand = c(0, 0)) +   # for both axes to remove unneeded padding
  coord_cartesian(clip = "off") + # to avoid clipping of the very top of the top ridgeline
  labs(
    x = "Redundancy",
    y = "Resolution"
  )

@@

**`r s_figure("grain-size")`**. Effect of grain size on sampling redundancy. (a), Percent of grid cells with redundancy > 0.5 by grain size (side length of square grid cells set to 10 km, 20 km, 30 km, or 40 km). (b), Percent of grid cells with redundancy = 0 by grain size. (c), Distribution of redundancy values by grain size. There is a sudden improvement in redundancy values from 10 km to 20 km, but less improvement as grain size is increased beyond 20 km.
